---
title: "final_project"
author: "Colin Pi"
date: '2018 5 28 '
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(car)
library(lmtest)
library(orcutt)
library(sandwich)
library(stargazer)
```

```{r, warning=FALSE, message=FALSE}
## Import the income classification data of countries coded by World Bank
income <- read_excel("CLASS.xls", skip = 3)[-1,] %>% select(Economy, `Income group`)
names(income)[1:2] <- c("Country","Income")

## Import World Bank Data and make some adjustment in variable names, such as year variables and country code. 
WBData <- read.csv("WBData.csv")[-c(131:135),]
names(WBData)[5:62] <- seq(1960,2017)
names(WBData)[3:4] <- c("Country","Code")

## Function of making wide version of data into narrower version
narrow <- function(i){
  outcome <- gather(WBData %>% filter(Series.Name == levels(WBData$Series.Name)[i]), key = Year, value = UQ(levels(WBData$Series.Name)[i]), 5:62) %>% select(6)
  return(outcome)
}

## Create a narrow version of World Bank Data
WBNarrow <- gather(WBData %>% 
                     filter(Series.Name == levels(WBData$Series.Name)[2]), 
                   key = Year, value = UQ(levels(WBData$Series.Name)[2]), 5:62) %>% 
  select(-c(1:2)) %>% bind_cols(lapply(c(3,5:6,8), narrow) %>% bind_cols())

## Coerce the character variable into numeric
WBNarrow[,4:8] <- sapply(WBNarrow[,4:8], as.numeric)

## Change the variable names in forms can be used for modeling
names(WBNarrow)[4:8] <- 
  c("Growth", "Health","Education", "Capital", "Trade")

## Join the World Bank Data and Income data
WBNarrow <- left_join(WBNarrow, income)

## Coerce the character variable into numeric
WBNarrow$Year <- as.numeric(WBNarrow$Year)
```

## CPI Index

```{r, warning=FALSE, message=FALSE}
## Import CPI data of 2017
cpi_2017 <- read_excel("CPI2017_FullDataSet.xlsx", skip=2)
cpi_2017 <- cpi_2017 %>% select(1,4)
names(cpi_2017)[2] = "2017"

## Import CPI data of 2016
cpi_2016 <- read_excel("CPI2016_FullDataSetWithRegionalTables.xlsx")
cpi_2016 <- cpi_2016 %>% select(1:2)
colnames(cpi_2016)[2] = "2016"

## Join CPI data of 2016 and 2017
cpi_2016_17 <- full_join(cpi_2016,cpi_2017, by = "Country")
cpi_2016_17 <- cpi_2016_17[-(181:182),]

## Import CPI data of 1998-2015
cpi_1998_2015 <- read_excel("CPI1998-2015.xlsx")

## Join CPI data of 1998-2015 and 2016-17
cpi_total <- full_join(cpi_1998_2015, cpi_2016_17, by = "Country")

## Since numeric data are framed as character, we changed them into numeric
cpi_total[,2:21] <- sapply(cpi_total[,2:21],as.numeric)

## The scale of CPI from 1998-2015 is out of 10, but it changed to out of 100 from 2012. So we changed the scale to out of 100.
cpi_total <- cpi_total %>% mutate_at(.vars = vars(names(cpi_total)[2:15]), funs(.*10))

## Create the narrow version of the CPI data
CPI <- gather(data = cpi_total, key = Year, value = CPI, 2:21)

## Change Year variable into numeric from character
CPI$Year <- as.numeric(CPI$Year)
```

```{r, warning=FALSE, message=FALSE}
## Join World Bank Data and CPI into one data frame.
allData <- left_join(WBNarrow, CPI)
```

Dependent Variable
Growth: "Adjusted net national income per capita (annual % growth)"

Independent Variable
Education: "Government expenditure on education, total (% of government expenditure)"

Control Variable
Health: "Current health expenditure (% of GDP)"                                                          
Capital: "Gross capital formation (% of GDP)"                                                             
Trade: "Trade (% of GDP)"
CPI: "Corruption Perception Index"

## Growth v. Education

```{r, warning=FALSE, message=FALSE}
ggplot(allData, aes(x = Education, y = Growth)) + 
  geom_point() +
  geom_smooth(method = "lm") + 
  scale_x_continuous(limits = c(0,25)) +
  labs(x = "Education Expenditure (% of Govt Expenditure)", y = "Annual Growth Rate per Capita (%)", title = "Growth Rate v. Education Expenditure")
```

## Fixed Effect

```{r, warning=FALSE, message=FALSE}
ggplot(allData, aes(x = Education, y = Growth, color = Income)) + 
  geom_smooth(method = "lm") + 
  labs(x = "Education Expenditure (% of Govt Expenditure)", y = "Annual Growth Rate per Capita (%)", title = "Growth Rate v. Education Expenditure")
```

## Check for Necessary Transformation and Potential Multicollinearity

```{r}
scatterplotMatrix(allData[c(4:8,10)])
```

Trade variable may be logged. Except that there is no need to transformation. Also there seems no multicollinearity issue either. 

## Model

#### Bivariate Model (Growth v. Education) ####

```{r}
bivariate.lm <- lm(Growth~Education, data = allData)
summary(bivariate.lm)
```

We can see a significant positive relation between both variables. 

#### Full model ####

```{r}
growth.lm <- lm(Growth ~ log(Trade) + Health + Capital + CPI + factor(Income) + Education, data = allData)
summary(growth.lm)
```

#### Restricted model ####

```{r}
growth.lm2 <- lm(Growth ~ Health + Capital + CPI + factor(Income) + Education, data = na.omit(allData))
summary(growth.lm2)
```

We got rid of the Trade variable (the p-value for this coefficient is too big).

## Multicollinearity

```{r}
vif(growth.lm2)
```

No evidence of multicollinearity. 

## Heteroscedasity

#### Graphical Method ####

```{r}
ggplot(growth.lm2, aes(x=na.omit(allData)$Education, y=.resid)) + 
  geom_jitter() +
  geom_hline(yintercept=0, col="red", linetype="dashed") +
  labs(title = "Residual vs Education", x="Education", y = "Residuals")
```

Not sure whether there is a notable heteroscedasity issue. 

#### GQ test ####

```{r}
gqtest(growth.lm2, fraction = 4, order.by = na.omit(allData)$Education)
```

We can find the evidence of heteroscedasity. 

## Autocorrelation

Because it is a timeseries data, we may suspect there is the autocorrelation issue. 

#### Graphical Methods ####

```{r}
ggplot(growth.lm2, aes(x=na.omit(allData)$Year, y=.resid)) + 
  geom_jitter() +
  geom_hline(yintercept=0, col="red", linetype="dashed") +
  labs(title = "Residual vs Year", x="Year", y = "Residuals")
```

#### Durbin-Watson, BG test ####

```{r}
dwtest(growth.lm2, order.by = na.omit(allData)$Year)
bgtest(growth.lm2, order.by = na.omit(allData)$Year)
```

#### Cochrane Orcutt ####

```{r}
growth.orcutt <- cochrane.orcutt(growth.lm2)
summary.orcutt(growth.orcutt)
```

The problem with Cochrane Orcutt is that we cannot address for heteroscedasity.

#### Newey West ####

```{r}
growth.newey <- coeftest(growth.lm2, vcov = NeweyWest(growth.lm))
growth.newey
```

Newey West deals with both heteroscedasity and autocorrelation. The problem is the Orcutt model is better than this version. Still Education coefficient is significant.
